\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Document requirements of the product}
\author{jose.chavez@utec.edu.pe \\ sergio.carbone@utec.edu.pe\\antonio.toche@utec.edu.pe\\jeffrey.orihuela@utec.edu.pe\\fernando.socualaya@utec.edu.pe}
\date{April 2019}

\begin{document}

\maketitle

\section{Target user profile and value proposition}
   In our project, we have two main objective users. The first is a user of YAPE that usually goes to MYPES and PYMES(micro and small business). The other is a YAPE user owner of a MYPES or PYMES(micro and small business).\\ Both have a big liking of technology and constantly look for new ways of digitizing all the process of selling taking advantage of these tools that streamline, secure and facilitate the shopping and sales.\\
   The main value proposal from our team is to add the feature of make possible to emit a ticket or invoice when you pay through YAPE instantly.
    \subsection{User Stories} 
    \begin{itemize}
    \item As the owner of a MYPE, I can organize all the tickets so that makes easier the procedures with SUNAT
    \item As the owner of a MYPE, I can recive information about the sales during the days of the week so that let me distribute better the resources.
    \item As a client, I want to be able to see my expenses organized so that I can better invest my money and not make unnecessary expenses.
    \item As a customer, I want to be able to pay without cash so I do not receive fake money.
    \item As a client I would like to be able to divide the account among several people in order to facilitate the payment.


    \end{itemize}
    
\section{Use cases}
\begin{enumerate}

\item As a client, I want to have electronic invoices or bills to be sure that I will never lose any.
   \begin{itemize}
        \item \textbf{Software System :} Yape 
        \item \textbf{Actor: } Client
        \item \textbf{Use Case : } Generate electronic bill
        \begin{enumerate}
            \item Client scans transaction QR code
            \item Yape collects transaction data
            \item Yape makes a request to SUNAT servers
            \item Yape generates and sends the pdf to the Client
            \item Yape awaits the response from the SUNAT BDD\\
            Use Case ends.
        \end{enumerate}
    \end{itemize}

    \item As the owner of a MYPE, I would like to keep a record of my clients in order to recognize them and build loyalty.
    \begin{itemize}
        \item \textbf{Software System :} Yape
        \item \textbf{Actor: } MYPE owner , Client
        \item \textbf{Use Case : } Save frequent clients 
        \begin{enumerate}
            \item Client makes payment
            \item MYPE owner receives payment 
            \item Yape saves Client transactions counter            
            \item adding one to client counter
            \item Update counters
            \item List clients with more transactions \\
            Use Case ends.
        \end{enumerate}
    \end{itemize}
    
    
%    \item .
%   \begin{itemize}
%        \item \textbf{Software System :} 
%        \item \textbf{Actor: } 
%        \item \textbf{Use Case : } 
%        \begin{enumerate}
%            \item .\\
%            Use Case ends.
%        \end{enumerate}
%    \end{itemize}


 %\item .
 %  \begin{itemize}
 %       \item \textbf{Software System :} 
 %       \item \textbf{Actor: } 
 %       \item \textbf{Use Case : } 
 %       \begin{enumerate}
 %           \item .\\
 %           Use Case ends.
  %      \end{enumerate}
 %   \end{itemize}
    
%    \item .
%   \begin{itemize}
%        \item \textbf{Software System :} 
%        \item \textbf{Actor: } 
%       \item \textbf{Use Case : } 
%        \begin{enumerate}
%            \item .\\
%            Use Case ends.
%        \end{enumerate}
%    \end{itemize}
    
\end{enumerate}

\section{Non-functional requirements}
\begin{enumerate}
    \item To be able to organize, according to sector, the payments made by each user.
     \item Take a register of the consumers and analyze the most concurrent days and of the highest demand.
     \item Accept within the tip payment or be in the ability to divide the account into a certain number of people.
     \item To be able to support payments of orders at home.
     \item Conclude the procedure with SUNAT in real time.
     \item Categorize the type of product or service sold.
    
\end{enumerate}

\section{Glossary}

\begin{itemize}
    \item MYPE/PYME: Micro and Small sized enterprises.
    \item MYPE Customer: The person who purchase a product in a MYPE.
    \item MYPE owner: The person who owns/manages a MYPE.
    \item Ticket/invoice: Payment vouchers.
    \item SUNAT: Entity that collect taxes.
\end{itemize}


\section{Product survey}
A product very similar to YAPE exists on Interbank . This product is called TUNKI and so as YAPE also allows you to make payments using only a phone number.
Both have the same functions of making payments and collections from the
same application to your contacts or scanning a QR code. In the case of
companies, they can also make payments to these through the scanner a
QR code. Although both applications have the same functionalities,
YAPE for its benefit is more recognized in the market and has had a better
diffusion. However, none of the applications has anything similar to
YACKET and include as part of YAPE could give a clear added value
for this innovative tool.



\end{document}

